### 2017-09-27 TF-vldb2018/sec-intro.tex

Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
the {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts in $G$ such that each satisfies the skill requirements of the task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (1) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(2) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number individuals with a specific skill in a team, and an upper bound of the team members, respectively.

@@

\revise{One can verify that none of existing methods suffice to identify the above desired team.
They can only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13} in search condition (1),
while cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints in search condition (2) (see details in Example~\ref{exa-teamF}).}
 \end{example}

@@

Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Intuitively, patterns $P$ capture the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem. As shown in Fig.~\ref{fig-motivation-example},  the desired team requirement can be expressed by the pattern graph $P_1$ (ignore dashed edges), such that the nodes represent the skill requirements, the edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

@@

\sstab{(1)} When the manager get the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
she may find $P_1$ is too restrictive to find possible matches.
Therefore, she enters a pattern update $\Delta P_1$ on $P_1$, composed of an edge 
deletion $(\kw{SD},\kw{ST})^-$.
We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
%\looseness=-1

@@

\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting considered so far.}

>>>>

Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
the {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts in $G$ such that each satisfies the skill requirements of the task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (1) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(2) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.

@@

\revise{One can verify that none of existing methods suffice to identify the above desired teams.
They can only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13} in search condition (1),
while cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints in search condition (2) (see details in Example~\ref{exa-teamF}).}
 \end{example}

@@

Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Intuitively, patterns $P$ captures the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem. As shown in Fig.~\ref{fig-motivation-example},  the desired team requirement can be expressed by the pattern graph $P_1$ (ignore dashed edges), such that the nodes represent the skill requirements, the edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

@@

\sstab{(1)} When the manager gets the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
she may find $P_1$ is too restrictive to find sensible matches.
Therefore, she enters a pattern update $\Delta P_1$ on $P_1$, composed of an edge 
deletion $(\kw{SD},\kw{ST})^-$.
We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
%\looseness=-1

@@

\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting studied so far.} 
\looseness = -1
